### 2020-10-11 priority-cp.tex
Added scheduler. Made reasonable progress.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{scheduler}
  \vspace{-4mm}
  \caption{Cyclic Scheduler from \cite{dardhagay18}}
  \label{fig:scheduler}
  \vspace{-4mm}
  \end{figure}

\subsection{Syntax}

@@

\paragraph*{Terms}
We let $\tm{P}, \tm{Q}$ range over processes, produced by the following grammar.
\[
\begin{array}[t]{lcl}
  \tm{P}, \tm{Q}
  & \coloneqq & \tm{\link{x}{y}}
         \sep   \tm{\res{x}{y}{P}}
         \sep   \tm{(\ppar{P}{Q})}
         \sep   \tm{\halt}
  \\   & \sep & \tm{\send{x}{y}{P}}
         \sep   \tm{\close{x}{P}}
         \sep   \tm{\recv{x}{y}{P}}
         \sep   \tm{\wait{x}{P}}
  \\   & \sep & \tm{\inl{x}{P}}
         \sep   \tm{\inr{x}{P}}
         \sep   \tm{\offer{x}{P}{Q}}
         \sep   \tm{\absurd{x}}
\end{array}
\]
Process $\tm{\link{x}{y}}$ links channels $x$ and $y$ and forwards communication from one to the other. $\tm{\res{x}{y}{P}}$, $\tm{(\ppar{P}{Q})}$ and $\tm{\halt}$ denote respectively the restriction processes where channel endpoints $\tm{x}$ and $\tm{y}$ are bound together and with scope $\tm{P}$, the parallel composition of processes $\tm{P}$ and $\tm{Q}$ and the terminated process.

@@

\subsection{Typing}
\input{fig/pcp-typing}

@@

\subsection{Example: Milner's Cyclic Scheduler}
We illustrate PCP with the cyclic scheduler~\cite{milner89}. The full typing for $\tm{\sched}$ is given in \cite{dardhagay18}.

We consider a simplified version: a set of 3 agents $\tm{\agent0}, \tm{\agent1}, \tm{\agent2}$ is scheduled to perform a certain task in cyclic order, starting with $\tm{\agent0}$. $\tm{\agent1}$ and $\tm{\agent2}$ send the result of some computation a collector process, respectively $\tm{\collector1}$ and $\tm{\collector2}$, before transmitting data further to the next agent in the cycle, being $\tm{\agent{(i+1)\bmod 3}}$. At the end of the round, $\tm{\agent0}$ send the final result of the computation to its collector $\tm{\collector0}$.

In line with the logical consistency requirements of the Curry-Howard correspondence, we define a finite version of Milner's scheduler, which executes one round of communication.
$$
\begin{array}{rcll}
  \tm{\sched}
  & \defeq
  & \tm{
    \res{x_0}{x'_0}{\res{x_1}{x'_1}{\res{x_2}{x'_2}{
    \res{\overrightarrow{y_0}}{\overleftarrow{y_1}}{
    \res{\overrightarrow{y_1}}{\overleftarrow{y_2}}{
    \res{\overrightarrow{y_2}}{\overleftarrow{y_0}}{}}}}}}
    }\\
  &
  & \tm{(\ppar{\agent0}{\ppar{\agent1}{\ppar{\agent2}{\ppar{\collector0}{\ppar{\collector1}{\collector2}}}}})}\\
  \tm{\agent0}
  & \defeq
  & \tm{\usend{\overrightarrow{y_0}}{d_0}{\recv{\overleftarrow{y_0}}{d'_0}{\usend{x_0}{d'_0}{
    \wait{\overleftarrow{y_0}}{\close{\overrightarrow{y_0}}{\close{x_0}{\halt}}}}}}} \\
  \tm{\agent{i}}
  & \defeq
  & \tm{\recv{\overleftarrow{y_i}}{d_i}{\usend{x_i}{d_i}{\recv{x_i}{d'_i}{\usend{\overrightarrow{y_i}}{d'_i}{
    \wait{\overleftarrow{y_i}}{\close{\overrightarrow{y_i}}{\close{x_i}{\halt}}}}}}}}
  & i \in \{1,2\} \\
  \tm{\collector{i}}
  & \defeq & \tm{\recv{x'_i}{d_i}{Q_i}}
  & i \in \{0,1,2\}
\end{array}
$$
In the above process, channels $\tm{d_i}$ and $\tm{d'_i}$ represent the data being transmitted. For simplicity, let them be channels of a terminated type. The processes $\tm{Q_i}$ represent the inner workings of the collector processes, each of which must eventually send back a response over $\tm{x'_i}$ and close the channel.
\subsection{Operational Semantics}
\input{fig/pcp-operational-semantics}

@@

\subsection{Metatheory}

@@

\begin{definition}[Actions]
  A~process acts on an endpoint $\tm{x}$ if it is in one of the following forms:
  \begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
    \item $\tm{\link{x}{y}}$ 
    \item $\tm{\link{y}{x}}$
    \item $\tm{\send{x}{y}{P}}$
    \item $\tm{\recv{x}{y}{P}}$
    \item $\tm{\close{x}{P}}$
    \item $\tm{\wait{x}{P}}$
    \item $\tm{\inl{x}{P}}$
    \item $\tm{\inr{x}{P}}$
    \item $\tm{\offer{x}{P}{Q}}$
    \item $\tm{\absurd{x}}$
    \end{itemize}
  \end{multicols}
  \noindent
  A~process is an action if it acts on some endpoint $\tm{x}$.
\end{definition}

\begin{definition}[Canonical Forms]
  \label{def:pcp-canonical-forms}
  A~process $\tm{P}$ is in canonical form if it is in one of the following forms:
  \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
  \item
    $\tm{\halt}$
  \item
    $\tm{\res{x_1}{x'_1}{\dots\res{x_n}{x'_n}{(P_1 \parallel\dots\parallel P_m)}}}$
    where $m>0$ and each $\tm{P_j}$ is an action.
  \end{itemize}
\end{definition}

\begin{restatablelemma}{lempcpcanonicalforms}[Canonical Forms]
  \label{lem:pcp-canonical-forms}
  If $\seq{P}{\ty{\Gamma}}$, there exists some $\tm{Q}$ such that $\tm{P}\equiv\tm{Q}$ and $\tm{Q}$ is in canonical form.
\end{restatablelemma}
\begin{proof}
  If $\tm{P}=\tm{\halt}$, we are done. Otherwise, we move any $\nu$-binders to the top using \LabTirName{SC-ResExt}, and discard any superfluous occurrences of $\tm{\halt}$ using \LabTirName{SC-ParNil}.
\end{proof}
\todo{We need to comment here why it is that we presented canonical forms, to start with...}
\begin{restatabletheorem}{thmpcpclosedprogress}[Closed Progress, $\red$]
  \label{thm:pcp-closed-progress}
  \hfill\\%newline before theorem statement
  If $\seq{P}{\emptyenv}$ and $\tm{P}$ is in canonical form, then either $\tm{P}=\tm{\halt}$ or there exists a $\tm{Q}$ such that $\tm{P}\red\tm{Q}$.
\end{restatabletheorem}
\begin{proof}
  Details in~\Cref{prf:thm-pcp-closed-progress}.
\end{proof}

>>>>

@@

\paragraph*{Terms}
We let $\tm{P}, \tm{Q}$ range over processes, produced by the following grammar.
\[
\begin{array}[t]{lcl}
  \tm{P}, \tm{Q}
  & \coloneqq & \tm{\link{x}{y}}
         \sep   \tm{\res{x}{y}{P}}
         \sep   \tm{(\ppar{P}{Q})}
         \sep   \tm{\halt}
  \\   & \sep & \tm{\send{x}{y}{P}}
         \sep   \tm{\close{x}{P}}
         \sep   \tm{\recv{x}{y}{P}}
         \sep   \tm{\wait{x}{P}}
  \\   & \sep & \tm{\inl{x}{P}}
         \sep   \tm{\inr{x}{P}}
         \sep   \tm{\offer{x}{P}{Q}}
         \sep   \tm{\absurd{x}}
\end{array}
\]
The process $\tm{\link{x}{y}}$ links endpoints $x$ and $y$ and forwards communication from one to the other. $\tm{\res{x}{y}{P}}$, $\tm{(\ppar{P}{Q})}$ and $\tm{\halt}$ denote respectively the restriction processes where channel endpoints $\tm{x}$ and $\tm{y}$ are bound together and with scope $\tm{P}$, the parallel composition of processes $\tm{P}$ and $\tm{Q}$ and the terminated process.

@@

\paragraph{Typing}
\input{fig/pcp-typing}

@@

\paragraph{Example: Milner's Cyclic Scheduler}
\[
  \begin{array}{lrlr}
    \tm{\sched}
    & \defeq & \tm{\res{a_1}{a'_1}{\dots{\res{a_n}{a'_n}{}}}}
               \tm{\res{b_1}{b'_1}{\dots{\res{b_n}{b'_n}{}}}}
               \tm{\res{c_1}{c'_1}{\dots{\res{c_n}{c'_n}{}}}}
               \tm{\res{d}{d'}{}}
    \\ &     & \tm{(
               \ppar{\proc1}{\agent1}
               \parallel
               \prod_{2\leq{i}\leq{n}}(\ppar{\proc{i}}{\wait{c'_{i-1}}{\agent{i}}})
               )}
    \\
    \tm{\agent1}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\wait{c'_n}{\close{d}{\halt}}}}}}
    \\
    \tm{\agent{i}}
    & \defeq & \tm{\close{a_i}{\wait{b_i}{\close{c_i}{\halt}}}}
    \\
    \tm{\proc{i}}
    & \defeq & \tm{\wait{a'_i}{\plug{P_i}{\close{b'_i}{Q_i}}}}
  \end{array}
\]

\paragraph{Operational Semantics}
\input{fig/pcp-operational-semantics}

@@

\paragraph{Metatheory}

@@

\begin{restatabletheorem}{thmpcpclosedprogress}[Closed Progress, $\red$]
  \label{thm:pcp-closed-progress}
  \hfill\\%newline before theorem statement
  If $\seq{P}{\emptyenv}$, then either $\tm{P}=\tm{\halt}$ or there exists a $\tm{Q}$ such that $\tm{P}\red\tm{Q}$.
\end{restatabletheorem}
\begin{proof}
  Details in~\Cref{prf:thm-pcp-closed-progress}.
\end{proof}
